\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin = 1in]{geometry}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{booktabs}
\usepackage{tabularray}
\usepackage[labelfont=bf, skip=5pt, font=small]{caption}
\usepackage{subcaption}
\usepackage{graphicx, float}
\graphicspath{{images/}}
\usepackage{fancyhdr}
\usepackage[style=chem-acs, articletitle=true]{biblatex}
% \addbibresource{references.bib}




\setlength{\parskip}{1em}
\setlength{\parindent}{0em}

\begin{document}

\begin{center}
	\huge{Hops River Radio Club}\\[10pt]
	\large{February 2025 Meeting Minutes}
\end{center}
\rule{\textwidth}{0.5pt}
	\noindent Members in Attendance: Christian, KD0POO; Alex, N1SIX; Steve, NK1V; George, KE1BT; Joe, N1EAI; Lisa, KB1RVU; Mary, WX1W; Dave, AC1K;
    
\rule{\textwidth}{0.5pt}

Called to Order: \textbf{18:00}
\section{Old Business}
    \begin{enumerate}
        \item Two meter net
            \begin{itemize}
                \item The net is going well.There were 8 who people attended last week.
                \item Repeater back up and is working reliable.
            \end{itemize}
        \item Christian installed as secretary
        \item Tenth anniversary
            \begin{itemize}
                \item Coming up in September. Need to plan something special.
            \end{itemize}
        \item Field Day
            \begin{itemize}
                \item Last full weekend of June (28 and 29 June 2025)
                \item Try to hold event at Burnt Hill Park, Hebron - has a pavilion. If we can't use the pavilion, we should check with other community parks/pavilions.
            \end{itemize}
    \end{enumerate}
\section{New Business}
    \begin{enumerate}
        \item RadioQTH (dot) net
            \begin{itemize}
                \item Website of license callsigns soon to be coming available
            \end{itemize}
        \item Treasury
            \begin{itemize}
                \item 558 dollars in the bank account
                \item Insurance paid until Sept or Oct.
            \end{itemize}
        \item Mary brought a box of goodies from Mike Donnelly
        \item Member updates
            \begin{itemize}
                \item Don Wilson is doing well in his recovery from his fall and is still living with his daughter.
                \item Mike Donnelly had hand surgery recently and is recovering. Mike was also recently diagnosed with cancer and is currently receiving treatment.
            \end{itemize}
    \end{enumerate}

Meeting end: \textbf{19:20}
\end{document}