\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin = 1in]{geometry}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{booktabs}
\usepackage{tabularray}
\usepackage[labelfont=bf, skip=5pt, font=small]{caption}
\usepackage{subcaption}
\usepackage{graphicx, float}
\graphicspath{{images/}}
\usepackage{fancyhdr}
\usepackage[style=chem-acs, articletitle=true]{biblatex}
% \addbibresource{references.bib}




\setlength{\parskip}{1em}
\setlength{\parindent}{0em}

\begin{document}

\begin{center}
	\huge{Hops River Radio Club}\\[10pt]
	\large{February 2026 Meeting Minutes}
\end{center}
\rule{\textwidth}{0.5pt}
	\noindent Members in Attendance: Christian, KD0POO; Dave, AC1K; Georg, K1YBO; Joe, KC1YRH; Steve, NK1V; Lora, KC1YCM; Karl, N1KJK; Mary, WX1W;

\rule{\textwidth}{0.5pt}

Called to Order: \textbf{18:16}

\section{Old Business}
    \begin{enumerate}
    \item Member Update
        \begin{itemize}
            \item  Joe (KC1YRH) is officially a member of the club! Welcome!
        \end{itemize}
    \item Treasury
        \begin{itemize}
            \item No change
        \end{itemize}
    \item Nets
        \begin{itemize}
            \item Do we want to do a net control rotation for the Wednesday 2m net?
        \end{itemize}
    \item General
        \begin{itemize}
            \item Georg is putting together a new ham welcome packet based on what Larry (K1HEJ) put together years ago. The packet is generic enough that different clubs can hand out at their VE sessions after a new ham passes their exam.
            \item POTA does a support your local parks event a couple times a year that would be a good time for a demonstration. April 18th is the next event. Steve is looking into locations that would work well. He'll send an email around with the details.
        \end{itemize}
    \end{enumerate}

\section{New Business}
    \begin{enumerate}
    \item Member Update
        \begin{itemize}
            \item  No update.
        \end{itemize}
    \item Treasury
        \begin{itemize}
            \item Balance at $\mathdollar 466$ for the club account.
        \end{itemize}
    \item Nets
        \begin{itemize}
            \item Georg offered to be apart of the net control rotation.
        \end{itemize}
    \item Field Day
        \begin{itemize}
            \item Field day is June 27th and 28th. We for sure will opperate on the 27th, unsure about the 28th.
            \item Mary is going to ask the senior center director to ask if we can use the Andover Senior Center for field day again. 
        \end{itemize}
    \item General
        \begin{itemize}
            \item POTA demo event happening April 18th. Need to decide on location: Day Pond, Salt Rock State Forrest, others?
                \begin{itemize}
                    \item Decision was made to meet at Day Pond by Colchester on April 18th at 10:00 AM. Operate for about four (4) hours, weather permitting.
                    \item Purchase a sandwich platter for lunch.
                \end{itemize}
        \end{itemize}
    \end{enumerate}

    \textbf{\Large{Next Club Meeting is 13 May 2026.}}

    Meeting end: \textbf{19:00}
\end{document}