\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin = 1in]{geometry}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{booktabs}
\usepackage{tabularray}
\usepackage[labelfont=bf, skip=5pt, font=small]{caption}
\usepackage{subcaption}
\usepackage{graphicx, float}
\graphicspath{{images/}}
\usepackage{fancyhdr}
\usepackage[style=chem-acs, articletitle=true]{biblatex}
% \addbibresource{references.bib}




\setlength{\parskip}{1em}
\setlength{\parindent}{0em}

\begin{document}

\begin{center}
	\huge{Hops River Radio Club}\\[10pt]
	\large{October 2025 Meeting Minutes}
\end{center}
\rule{\textwidth}{0.5pt}
	\noindent Members in Attendance: Christian, KD0POO; Mary, WX1W; Lisa, KB1RVU; George, K1YBO; Steve, NK1V; Dave, AC1K; Bob, KC1ACK; Lora, KC1YCM; Karl, N1KJK;

\rule{\textwidth}{0.5pt}

Called to Order: \textbf{18:05}

\section{Old Business}
    \begin{enumerate}
    \item Member Update
        \begin{itemize}
            \item Carrol Bowen showed up to the August meeting and is reading through the tech. manual. 
        \end{itemize}
    \item Treasury
        \begin{itemize}
            \item It's time for dues! $\mathdollar 20$ for the year.
            \item We have $\mathdollar 436$ in the bank account. After insurance, we should have $\mathdollar 236$.
        \end{itemize}
    \item Nets
        \begin{itemize}
            \item The Wednesday night net has died off for the most part - likely due the summer.
        \end{itemize}
    \item Anniversary
        \begin{itemize}
            \item Mary presented the anniversary logo concept developed at the August meeting. Logo needs to be cleaned up into a form that can be embroidered.
            \item Mary renewed the club's license - good for another 10 years.
        \end{itemize}
    \item General
        \begin{itemize}
            \item George presented the idea to develop resources to help disabled people get on the air. He mentioned the Handy Hams out of Minnesota as an example.
            \item George shared a Ham Radio social breakfast he's organizing at Athenian in Middletown, CT on Oct. 18th.
        \end{itemize}
    \end{enumerate}

\section{New Business}
    \begin{enumerate}
    \item Member Update
        \begin{itemize}
            \item  Lora is now an ARRL member! Congrats to her!
        \end{itemize}
    \item Treasury
        \begin{itemize}
            \item We have had 9 members renewed dues and paid our annual insurance to ARRL. This leaves us at $\mathdollar 396$.
        \end{itemize}
    \item Nets
        \begin{itemize}
            \item Mary took over net control for a couple of weeks, but no one checked in. She thinks the lack of traffic was due to people being outside/active during that time. Mary proposed to turn it into a seasonal net.
        \end{itemize}
    \item Anniversary
        \begin{itemize}
            \item George tweaked the logo design from Mary and presented them to the club.
        \end{itemize}
    \item General
        \begin{itemize}
            \item Handy Hams has been very well received by other clubs. The ARRL does very little to help the disabled with operating, so George has made it his mission to ensure Connecticut hams are aware of the program and how to get involved.
            \item Traffic Handlers social breakfast at the Athenian in Middletown, CT on Oct. 18th. All are welcome, not just net traffic handlers. Ethel Kramer, KB1NMO, net manager for WestConn net, will be there.
            \item Lisa's 2m antenna is down and is looking for ideas for a new antenna and grounding.
            \item Lisa's question: In a simple explanation, what is simplex? It's a set of designated calling frequencies for direct radio-radio communication without the aid of repeaters.
            \item Mary's question: Should we apply for a LotW certificate for the club call sign, K1HRR? Club's decision was to go ahead with obtaining the certificate.
        \end{itemize}
    \end{enumerate}

    Meeting end: \textbf{19:00}
\end{document}