\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin = 1in]{geometry}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{booktabs}
\usepackage{tabularray}
\usepackage[labelfont=bf, skip=5pt, font=small]{caption}
\usepackage{subcaption}
\usepackage{graphicx, float}
\graphicspath{{images/}}
\usepackage{fancyhdr}
\usepackage[style=chem-acs, articletitle=true]{biblatex}
% \addbibresource{references.bib}




\setlength{\parskip}{1em}
\setlength{\parindent}{0em}

\begin{document}

\begin{center}
	\huge{Hops River Radio Club}\\[10pt]
	\large{November 2025 Meeting Minutes}
\end{center}
\rule{\textwidth}{0.5pt}
	\noindent Members in Attendance: Christian, KD0POO; Mary, WX1W; Lisa, KB1RVU; Dave, AC1K; Karl, N1KJK; Alex, N1SIX;

\rule{\textwidth}{0.5pt}

Called to Order: \textbf{18:08}

\section{Old Business}
     \begin{enumerate}
    \item Member Update
        \begin{itemize}
            \item  Lora is now an ARRL member! Congrats to her!
        \end{itemize}
    \item Treasury
        \begin{itemize}
            \item We have had 9 members renewed dues and paid our annual insurance to ARRL. This leaves us at $\mathdollar 396$.
        \end{itemize}
    \item Nets
        \begin{itemize}
            \item Mary took over net control for a couple of weeks, but no one checked in. She thinks the lack of traffic was due to people being outside/active during that time. Mary proposed to turn it into a seasonal net.
        \end{itemize}
    \item Anniversary
        \begin{itemize}
            \item George tweaked the logo design from Mary and presented them to the club.
        \end{itemize}
    \item General
        \begin{itemize}
            \item Handy Hams has been very well received by other clubs. The ARRL does very little to help the disabled with operating, so George has made it his mission to ensure Connecticut hams are aware of the program and how to get involved.
            \item Traffic Handlers social breakfast at the Athenian in Middletown, CT on Oct. 18th. All are welcome, not just net traffic handlers. Ethel Kramer, KB1NMO, net manager for WestConn net, will be there.
            \item Lisa's 2m antenna is down and is looking for ideas for a new antenna and grounding.
            \item Lisa's question: In a simple explanation, what is simplex? It's a set of designated calling frequencies for direct radio-radio communication without the aid of repeaters.
            \item Mary's question: Should we apply for a LotW certificate for the club call sign, K1HRR? Club's decision was to go ahead with obtaining the certificate.
        \end{itemize}
    \end{enumerate}

\section{New Business}
    \begin{enumerate}
    \item Member Update
        \begin{itemize}
            \item  Bill, KC1RUB, has been doing well. Relayed to Alex that he found out WJST-x released a new software and has been operating with it actively.
        \end{itemize}
    \item Treasury
        \begin{itemize}
            \item No update from Steve.
        \end{itemize}
    \item Nets
        \begin{itemize}
            \item No updates.
        \end{itemize}
    \item Anniversary
        \begin{itemize}
            \item Karl has a contact, Leanne Peters, who may be able to convert the club's proposed logo into something that can easily be embroidered. Mary also suggested reaching out to Pat, designed the previous club logo.
        \end{itemize}
    \item General
        \begin{itemize}
            \item Antenna build party for Lisa's 2m antenna. An email with details to follow.
            \item Karl asked about multi-band dipole options and layout suggestions for his property. Suggestions included a G5RV and a G5RV Jr.
            \item Lisa asked if the club was going to do winter field day.
            \item Lisa also inquired about a club POTA outing/demo for those who have never participated. Maybe those interested in POTA could tag along with Steve and see how an activation works.
            \item Karl asked if there is interested in him sourcing steel and welding drive-on antenna mast mounts.
        \end{itemize}
    \end{enumerate}

    \textbf{\Large{Next Club Meeting is 10 December 2025.}}

    Meeting end: \textbf{19:07}
\end{document}