\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin = 1in]{geometry}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{booktabs}
\usepackage{tabularray}
\usepackage[labelfont=bf, skip=5pt, font=small]{caption}
\usepackage{subcaption}
\usepackage{graphicx, float}
\graphicspath{{images/}}
\usepackage{fancyhdr}
\usepackage[style=chem-acs, articletitle=true]{biblatex}
% \addbibresource{references.bib}




\setlength{\parskip}{1em}
\setlength{\parindent}{0em}

\begin{document}

\begin{center}
	\huge{Hops River Radio Club}\\[10pt]
	\large{May 2025 Meeting Minutes}
\end{center}
\rule{\textwidth}{0.5pt}
	\noindent Members in Attendance: Christian, KD0POO; Steve, NK1V; Mary, WX1W; Dave, AC1K; Karl, N1KJK; Lisa, KB1RVU 
    
\rule{\textwidth}{0.5pt}

Called to Order: \textbf{18:15}
\section{Old Business}
\begin{enumerate}
    \item Member Update
        \begin{itemize}
            \item Don Wilson wanted to attend tonight, but can't drive. Living back in the community he was previously in, but on the first floor now.
        \end{itemize}
    \item Treasury
        \begin{itemize}
            \item No change. $\mathdollar 558$
        \end{itemize}
    \item Nets
        \begin{itemize}
            \item 2 meter net - 6 or 7 people last week. One new person
            \item 75 meter net - Johnny said he's suspending for a while due to unlicensed participants
        \end{itemize}
    \item Field Day
        \begin{itemize}
            \item Last full weekend of June ($28th-29th$)
            \item Dave suggested just using the Andover pickleball courts without explicit permission.
            \item Bob to check with Columbia pavilions
            \item Bring sandwich platters, chips, and other snack type foods
        \end{itemize}
\end{enumerate}

\section{New Business}
\begin{enumerate}
    \item Member Update
        \begin{itemize}
            \item Don will probably not make it to field day.
        \end{itemize}
    \item Treasury
        \begin{itemize}
            \item $\mathdollar 558$ in the Treasury
            \item Insurance due at the end of summer $\sim \mathdollar200$
            \item 13 Active members, 30 on the membership list.
        \end{itemize}
    \item Nets
        \begin{itemize}
            \item 2m net is going well and people are having a lot of fun. Averaging 5-9 members. Lisa is stepping down from net control in mid-July. If anyone is interested, they should contact Lisa.
            \item 
        \end{itemize}
    \item Field Day
        \begin{itemize}
            \item Mary has paper goods for field day, but people need to bring food.
            \item Mary and Dave grabbed a couple of ARRL fliers for the event to fill in local event details.
            \item Someone has a club sign to put in the lawn for advertisement (Mary?)
            \item Happening at the Andover Senior Center, 17 School Rd. Andover, CT.
            \item Someone should order a sandwich platter from Walmart/BJ's
            \item What about snacks?
            \item Logging? ARRL might have paper logs someone could print off
            \item Mary is bringing a generator, but we might not use for our contest designation.
        \end{itemize}
\end{enumerate}

Meeting End: \textbf{19:00}
\end{document}