\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin = 1in]{geometry}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{booktabs}
\usepackage{tabularray}
\usepackage[labelfont=bf, skip=5pt, font=small]{caption}
\usepackage{subcaption}
\usepackage{graphicx, float}
\graphicspath{{images/}}
\usepackage{fancyhdr}
\usepackage[style=chem-acs, articletitle=true]{biblatex}
% \addbibresource{references.bib}




\setlength{\parskip}{1em}
\setlength{\parindent}{0em}

\begin{document}

\begin{center}
	\huge{Hops River Radio Club}\\[10pt]
	\large{May 2025 Meeting Minutes}
\end{center}
\rule{\textwidth}{0.5pt}
	\noindent Members in Attendance: Christian, KD0POO; Mary, WX1W; Lisa, KB1RVU; George, K1YBO; Alex, N1SIX; Steve, NK1V; Dave, AC1K; Lora, KC1YCM; Bob, KC1ACK;

\rule{\textwidth}{0.5pt}

Called to Order: \textbf{18:09}

\section{New Business}
\begin{enumerate}
    \item Member Update
        \begin{itemize}
            \item Carrol Bowen showed up to the August meeting and is reading through the tech. manual. 
        \end{itemize}
    \item Treasury
        \begin{itemize}
            \item It's time for dues! $\mathdollar 20$ for the year
            \item We have $\mathdollar 436$ in the bank account. After insurance, we should have $\mathdollar 236$.
        \end{itemize}
    \item Nets
        \begin{itemize}
            \item The Wednesday night net has died off for the most part - likely due the summer.
        \end{itemize}
    \item Anniversary
        \begin{itemize}
            \item Mary presented the anniversary logo concept developed at the August meeting. Logo needs to be cleaned up into a form that can be embroidered
            \item Mary renewed the club's license - good for another 10 years
        \end{itemize}
    \item General
        \begin{itemize}
            \item George presented the idea to develop resources to help disabled people get on the air. He mentioned the Handy Hams out of Minnesota as an example
            \item George shared a Ham Radio social breakfast he's organizing at Athenia in Middletown, CT on Oct. 18th
        \end{itemize}
\end{enumerate}

Meeting End: \textbf{18:36}

\end{document}