\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin = 1in]{geometry}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{booktabs}
\usepackage{tabularray}
\usepackage[labelfont=bf, skip=5pt, font=small]{caption}
\usepackage{subcaption}
\usepackage{graphicx, float}
\graphicspath{{images/}}
\usepackage{fancyhdr}
\usepackage[style=chem-acs, articletitle=true]{biblatex}
% \addbibresource{references.bib}




\setlength{\parskip}{1em}
\setlength{\parindent}{0em}

\begin{document}

\begin{center}
	\huge{Hops River Radio Club}\\[10pt]
	\large{February 2025 Meeting Minutes}
\end{center}
\rule{\textwidth}{0.5pt}
	\noindent Members in Attendance: Christian, KD0POO; Alex, N1SIX; Steve, NK1V; George, KE1BT; Joe, N1EAI; Lisa, KB1RVU; Mary, WX1W; Dave, AC1K; Johnny, KC1REJ
    
\rule{\textwidth}{0.5pt}

Called to Order: \textbf{18:00}
\section{Old Business}
    \begin{enumerate}
        \item Two meter net
            \begin{itemize}
                \item The net is going well.There were 8 who people attended last week.
                \item Repeater back up and is working reliable.
            \end{itemize}
        \item Christian installed as secretary
        \item Tenth anniversary
            \begin{itemize}
                \item Coming up in September. Need to plan something special.
            \end{itemize}
        \item Field Day
            \begin{itemize}
                \item Last full weekend of June (28 and 29 June 2025)
                \item Try to hold event at Burnt Hill Park, Hebron - has a pavilion. If we can't use the pavilion, we should check with other community parks/pavilions.
            \end{itemize}
        \item RadioQTH (dot) net
            \begin{itemize}
                \item Website of license callsigns soon to be coming available
            \end{itemize}
        \item Treasury
            \begin{itemize}
                \item 558 dollars in the bank account
                \item Insurance paid until Sept or Oct.
            \end{itemize}
        \item Mary brought a box of goodies from Mike Donnelly
        \item Member updates
            \begin{itemize}
                \item Don Wilson is doing well in his recovery from his fall and is still living with his daughter.
                \item Mike Donnelly had hand surgery recently and is recovering. Mike was also recently diagnosed with cancer and is currently receiving treatment.
            \end{itemize}
    \end{enumerate}

        February Meeting minutes approved.

\section{New Business}
    \begin{enumerate}
        \item Member Update
            \begin{itemize}
                \item Don Wilson recently had a seizure. He's been having issues with texting/ communicating/ processing.
                \item Bill set up and operating, but isn't meshing well with the local club.
                \item KB1EMJ let her license expire past the grace period and is looking to obtain her license again. If anyone has an extra, current technician manual she would appreciate using it.
            \end{itemize}
        \item Items available
            \begin{itemize}
                \item Lisa has 2 propane fryers for sale, $\$ 100$ each. Contact her if interested.
            \end{itemize}
        \item Contests Coming up
            \begin{itemize}
                \item 13 Colonies contest is looking for volunteers. If interested ask Lisa or Mary for details.
            \end{itemize}
        \item Field Day
            \begin{itemize}
                \item If we want to reserve the pavilion in Hebron, it needs to be made by a citizen.
            \end{itemize}
        \item Nets
            \begin{itemize}
                \item Johnny has a ``Welcome to the Weekend'' net on 80 m (3.969 MHz) that happens on Fridays $20:00$ est.
                \item Wednesday night 2 m ragchew net, Wednesday $18:30$ est (147.300  PL: 77.0).
            \end{itemize}
        \item Treasury
            \begin{itemize}
                \item No change.
            \end{itemize}
        \item Ideas
            \begin{itemize}
                \item George proposed a senior citizen outreach activity called ``Senior Center on the Air''.
            \end{itemize}
    \end{enumerate}

Meeting end: \textbf{19:14}
\end{document}