\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin = 1in]{geometry}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{booktabs}
\usepackage{tabularray}
\usepackage[labelfont=bf, skip=5pt, font=small]{caption}
\usepackage{subcaption}
\usepackage{graphicx, float}
\graphicspath{{images/}}
\usepackage{fancyhdr}
\usepackage[style=chem-acs, articletitle=true]{biblatex}
% \addbibresource{references.bib}




\setlength{\parskip}{1em}
\setlength{\parindent}{0em}

\begin{document}

\begin{center}
	\huge{Hops River Radio Club}\\[10pt]
	\large{February 2025 Meeting Minutes}
\end{center}
\rule{\textwidth}{0.5pt}
	\noindent Members in Attendance: Christian, KD0POO; Alex, N1SIX; Lisa, KB1RVU; Mary, WX1W; Dave, AC1K; Bob, ;
    
\rule{\textwidth}{0.5pt}

Called to Order: \textbf{18:12}
\section{Old Business}
\begin{enumerate}
    \item Meeting began at $18:00$.
    \item Member Update
        \begin{itemize}
            \item Don Wilson recently had a seizure. He's been having issues with texting/ communicating/ processing.
            \item Bill set up and operating, but isn't meshing well with the local club.
            \item KB1EMJ let her license expire past the grace period and is looking to obtain her license again. If anyone has an extra, current technician manual she would appreciate using it.
        \end{itemize}
    \item Items available
        \begin{itemize}
            \item Lisa has 2 propane fryers for sale, $\$ 100$ each. Contact her if interested.
        \end{itemize}
    \item Contests Coming up
        \begin{itemize}
            \item 13 Colonies contest is looking for volunteers. If interested ask Lisa or Mary for details.
        \end{itemize}
    \item Field Day
        \begin{itemize}
            \item If we want to reserve the pavilion in Hebron, it needs to be made by a citizen.
        \end{itemize}
    \item Nets
        \begin{itemize}
            \item Johnny has a ``Welcome to the Weekend'' net on 80 m (3.969 MHz) that happens on Fridays $20:00$ est.
            \item Wednesday night 2 m ragchew net, Wednesday $18:30$ est (147.300  PL: 77.0).
        \end{itemize}
    \item Treasury
        \begin{itemize}
            \item No change.
        \end{itemize}
    \item Ideas
        \begin{itemize}
            \item George proposed a senior citizen outreach activity called ``Senior Center on the Air''.
        \end{itemize}
    \item Meeting adjourned at $19:14$.
\end{enumerate}

Old business accepted unanimously.

\section{New Business}
\begin{enumerate}
    \item Member Update
        \begin{itemize}
            \item Dave's birthday today! DE49Lesso at gmail.com
            \item Carole recieved her manual and is studying for the test. Can hold a testing session at her house if she can't get out.
        \end{itemize}
    \item Field Day
        \begin{itemize}
            \item locations: ideas:
            \item Pickleball courts in Andover might be a backup location weather pending
            \item Columbia pickleball courts have a pavilion that might be viable. Closes at dusk. Bob to look into reserving the pavilion.
            \item Henikin road location?
        \end{itemize}
    \item Treasury
        \begin{itemize}
            \item Steve not present for report. Assumed no change in reserves.
        \end{itemize}
    \item Nets
        \begin{itemize}
            \item Doug, W1HNA, was able to tune into Johnny's cb net and is interested in expanding into cw, but is in restricted living.
        \end{itemize}
    \item Digital Modes
        \begin{itemize}
            \item WJST-X for FT8; you can call ``cq'' or hunt for other signals; additional discussion about how the FT8 works.
        \end{itemize}

\end{enumerate}
Meeting end: \textbf{some time}
\end{document}