\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin = 1in]{geometry}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{booktabs}
\usepackage{tabularray}
\usepackage[labelfont=bf, skip=5pt, font=small]{caption}
\usepackage{subcaption}
\usepackage{graphicx, float}
\graphicspath{{images/}}
\usepackage{fancyhdr}
\usepackage[style=chem-acs, articletitle=true]{biblatex}
% \addbibresource{references.bib}




\setlength{\parskip}{1em}
\setlength{\parindent}{0em}

\begin{document}

\begin{center}
	\huge{Hops River Radio Club}\\[10pt]
	\large{February 2026 Meeting Minutes}
\end{center}
\rule{\textwidth}{0.5pt}
	\noindent Members in Attendance: Christian, KD0POO; Mary, WX1W; Lisa, KB1RVU; Dave, AC1K; George, K1YBO; Joe, KC1YRH

\rule{\textwidth}{0.5pt}

Called to Order: \textbf{18:27}

\section{Old Business}
    \begin{enumerate}
    \item Member Update
        \begin{itemize}
            \item  No updates
        \end{itemize}
    \item Treasury
        \begin{itemize}
            \item $\mathdollar 466$ in the bank account.
            \item Insurance due in September/October.
        \end{itemize}
    \item Nets
        \begin{itemize}
            \item Anyone want to pick-up the net-control for the two-meter net?
            \item Maybe have people take turns (first and third or maybe once a month)?
        \end{itemize}
    \item General
        \begin{itemize}
            \item Approach the town of Andover about having field day at the senior center in June. Maybe two days this year - tearing down overnight?
            \item Christian set-up a GitHub repository to post the meeting minutes online. They'll send out the link with this month's meeting minutes.
        \end{itemize}
    \end{enumerate}

\section{New Business}
    \begin{enumerate}
    \item Member Update
        \begin{itemize}
            \item  No updates.
        \end{itemize}
    \item Treasury
        \begin{itemize}
            \item No updates.
        \end{itemize}
    \item Nets
        \begin{itemize}
            \item No update
        \end{itemize}
    \item General
        \begin{itemize}
            \item Antenna projects for Georg, Lisa, and others are on hold until snow clears up a bit.
            \item Georg asked if anyone in the club used DMR and if it was worth delving into. Club interest?
        \end{itemize}
    \end{enumerate}

    \textbf{\Large{Next Club Meeting is 11 March 2026.}}

    Meeting end: \textbf{18:51}
\end{document}