\documentclass[12pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin = 1in]{geometry}
\usepackage{amsmath, amssymb, amsthm}
\usepackage{booktabs}
\usepackage{tabularray}
\usepackage[labelfont=bf, skip=5pt, font=small]{caption}
\usepackage{subcaption}
\usepackage{graphicx, float}
\graphicspath{{images/}}
\usepackage{fancyhdr}
\usepackage[style=chem-acs, articletitle=true]{biblatex}
% \addbibresource{references.bib}




\setlength{\parskip}{1em}
\setlength{\parindent}{0em}

\begin{document}

\begin{center}
	\huge{Hops River Radio Club}\\[10pt]
	\large{February 2026 Meeting Minutes}
\end{center}
\rule{\textwidth}{0.5pt}
	\noindent Members in Attendance: Christian, KD0POO; Lisa, KB1RVU; Dave, AC1K; George, K1YBO; Joe, KC1YRH; Steve, NK1V; Lora, KC1YCM; Karl, N1KJK; 

\rule{\textwidth}{0.5pt}

Called to Order: \textbf{18:02}

\section{Old Business}
    \begin{enumerate}
    \item Member Update
        \begin{itemize}
            \item  No updates.
        \end{itemize}
    \item Treasury
        \begin{itemize}
            \item No updates.
        \end{itemize}
    \item Nets
        \begin{itemize}
            \item No update
        \end{itemize}
    \item General
        \begin{itemize}
            \item Antenna projects for Georg, Lisa, and others are on hold until snow clears up a bit.
            \item Georg asked if anyone in the club used DMR and if it was worth delving into. Club interest?
        \end{itemize}
    \end{enumerate}

\section{New Business}
    \begin{enumerate}
    \item Member Update
        \begin{itemize}
            \item  Joe (KC1YRH) is officially a member of the club! Welcome!
        \end{itemize}
    \item Treasury
        \begin{itemize}
            \item No change
        \end{itemize}
    \item Nets
        \begin{itemize}
            \item Do we want to do a net control rotation for the Wednesday 2m net?
        \end{itemize}
    \item General
        \begin{itemize}
            \item Georg is putting together a new ham welcome packet based on what Larry (K1HEJ) put together years ago. The packet is generic enough that different clubs can hand out at their VE sessions after a new ham passes their exam.
            \item POTA does a support your local parks event a couple times a year that would be a good time for a demonstration. April 18th is the next event. Steve is looking into locations that would work well. He'll send an email around with the details.
        \end{itemize}
    \end{enumerate}

    \textbf{\Large{Next Club Meeting is 08 April 2026.}}

    Meeting end: \textbf{19:08}
\end{document}